\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-04 paper.qmd
Update Figure 7

![](figures/scurve/sc_true_1.png)

![](figures/scurve/sc_true_2.png)

![](figures/scurve/sc_true_3.png)

@@

```{r}
## hexagon binning to have regular hexagons
hb_obj_scurve1 <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = 7, 
  r2 = r2,
  q = 0.05)

@@

```{r}
#| echo: false
#| label: fig-bins-scurve
#| fig-pos: H
#| fig-cap: "Hexbin density plots of UMAP layout of the S-curve data, using three different bin inputs: (a) $b = 91$ (7, 13), (b) $b = 190$ (10, 19), and (c) $b = 364$ (14, 26). Color indicates standardized counts, dark indicating high count and light indicates low count. At the smallest bin size the data segregates into two separate groups, suggesting this is too many bins. Using the MSE of the model fit in $p-D$ helps decide on a useful choice of number of bins."
#| fig-width: 6
#| fig-height: 3

>>>>

![](figures/scurve/sc_true_1.png){width="150" fig-align="center"}

![](figures/scurve/sc_true_2.png){width="150" fig-align="center"}

![](figures/scurve/sc_true_3.png){width="150" fig-align="center"}

@@

```{r}
## hexagon binning to have regular hexagons
hb_obj_scurve1 <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = 7, 
  r2 = r2)

@@

```{r}
#| echo: false
#| label: fig-bins-scurve
#| fig-pos: H
#| fig-cap: "Hexbin density plots of UMAP layout of the S-curve data, using three different bin inputs: (a) $b = 70$ (7, 10), (b) $b = 240$ (12, 20), and (c) $b = 322$ (14, 23). Color indicates standardized counts, dark indicating high count and light indicates low count. At the smallest bin size the data segregates into two separate groups, suggesting this is too many bins. Using the MSE of the model fit in $p-D$ helps decide on a useful choice of number of bins."
#| fig-width: 6
#| fig-height: 2.5

### 2024-07-04 paper.tex
Update Figure 7

\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_true_1.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_true_2.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_true_3.png}\end{minipage}%

@@

\caption{\label{fig-bins-scurve}Hexbin density plots of UMAP layout of
the S-curve data, using three different bin inputs: (a) \(b = 91\) (7,
13), (b) \(b = 190\) (10, 19), and (c) \(b = 364\) (14, 26). Color
indicates standardized counts, dark indicating high count and light
indicates low count. At the smallest bin size the data segregates into
two separate groups, suggesting this is too many bins. Using the MSE of
the model fit in \(p-D\) helps decide on a useful choice of number of
bins.}

>>>>

\begin{minipage}{0.33\linewidth}
\begin{center}
\includegraphics[width=1.5625in,height=\textheight]{figures/scurve/sc_true_1.png}
\end{center}
\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\begin{center}
\includegraphics[width=1.5625in,height=\textheight]{figures/scurve/sc_true_2.png}
\end{center}
\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\begin{center}
\includegraphics[width=1.5625in,height=\textheight]{figures/scurve/sc_true_3.png}
\end{center}
\end{minipage}%

@@

\caption{\label{fig-bins-scurve}Hexbin density plots of UMAP layout of
the S-curve data, using three different bin inputs: (a) \(b = 70\) (7,
10), (b) \(b = 240\) (12, 20), and (c) \(b = 322\) (14, 23). Color
indicates standardized counts, dark indicating high count and light
indicates low count. At the smallest bin size the data segregates into
two separate groups, suggesting this is too many bins. Using the MSE of
the model fit in \(p-D\) helps decide on a useful choice of number of
bins.}
